No Detectable Evidence of Genetic Associations with Anadromous and Resident Masu Salmon Sampled within Hokkaido

### 2022-06-01 paper/paper_draft.Rmd
IBS

```{r, eval=TRUE, include=FALSE}
mat <- read.table("../angsdput.covMat")
IBS <- data.table::fread("../angsdput.covMat")
nrow(IBS)
IBS <- IBS[-32,-c(97, 32)]
pca_r <- eigen(IBS)
pca <- pca_r$vectors
write.table(pca[,1:20], "pca20.txt", col.names = FALSE, row.names = FALSE, quote=FALSE, sep="\t")
colnames(pca) <- paste0("PC", 1:ncol(pca))
meta <- read.table("../data/sample_meta.txt", header = TRUE)[-32,]
pca <- cbind(pca, meta)

@@

The number of unfiltered reads are `r prettyNum(sort_read_count,big.mark=",",scientific=FALSE)`. After filtering, the number of reads were `r prettyNum(sort_flt_read_count,big.mark=",",scientific=FALSE)`. We called a total of `r prettyNum(number_snps_after_filtering,big.mark=",",scientific=FALSE)` SNPs and `r prettyNum(nrow(IBS),big.mark=",",scientific=FALSE)` IBS loci. 
<!-- flt read = `r sort_flt_read_count`  -->
<!-- flt read = 90449126 -->
<!-- unfiltered reads = `r sort_read_count`  -->
<!-- unfiltered reads = 163200129 -->
<!-- number of snps = `r number_snps_after_filtering` -->
<!-- Number of snps= 71175? -->
<!-- number of IBS loci = `r nrow(IBS)` -->

@@

We did not find any significant genetic associations with migratory phenotype (see Figure X). This indicates that in the streams we examined, there may not be any loci in the genome that strongly contribute to migratory life history decisions. It is not therefore surprising that the random forest which we conducted also did not have strong predictive power for anadromy and residency, since it would not be able to accurately group the individuals to their actual life history if there are no genetic elements that contribute to migratory phenotype.

>>>>

```{r, eval=TRUE, include=FALSE}
mat <- read.table("../angsdput.covMat")
IBS <- data.table::fread("../angsdput.covMat")
IBS.loci <- data.table::fread("../data/angsdput.ibs.gz")
nrow(IBS)
IBS <- IBS[-32,-c(97, 32)]
pca_r <- eigen(IBS)
pca <- pca_r$vectors
write.table(pca[,1:20], "pca20.txt", col.names = FALSE, row.names = FALSE, quote=FALSE, sep="\t")
colnames(pca) <- paste0("PC", 1:ncol(pca))
meta <- read.table("../data/sample_meta.txt", header = TRUE)[-32,]
pca <- cbind(pca, meta)

@@

The number of unfiltered reads are `r prettyNum(sort_read_count,big.mark=",",scientific=FALSE)`. After filtering, the number of reads were `r prettyNum(sort_flt_read_count,big.mark=",",scientific=FALSE)`. We called a total of `r prettyNum(number_snps_after_filtering,big.mark=",",scientific=FALSE)` SNPs and `r prettyNum(nrow(IBS.loci),big.mark=",",scientific=FALSE)` IBS loci. 
<!-- flt read = `r sort_flt_read_count`  -->
<!-- flt read = 90449126 -->
<!-- unfiltered reads = `r sort_read_count`  -->
<!-- unfiltered reads = 163200129 -->
<!-- number of snps = `r number_snps_after_filtering` -->
<!-- Number of snps= 71175? -->
<!-- number of IBS loci = `r nrow(IBS)` -->

@@

We did not find any significant genetic associations with migratory phenotype (see Figure 1). This indicates that in the streams we examined, there may not be any loci in the genome that strongly contribute to migratory life history decisions. It is not therefore surprising that the random forest which we conducted also did not have strong predictive power for anadromy and residency, since it would not be able to accurately group the individuals to their actual life history if there are no genetic elements that contribute to migratory phenotype.
